Parsing Postfix Log Files

### 2009-08-26 doc/logparser-other-parsers-review.tex
Changes made to improve appearance after switching to one-and-a-half spacing.
Changes to capitalisation of titles, as specified by Howard Hamilton. Fixed that/than type identified by Joe Carthy.
Corrections from Howard Hamilton: * Added a brief introduction to MySQL. * Removed the MySQL-BerkeleyDB comparison, because I didn't think it was   appropriate.  Howard's instruction was to move it into a separate paragraph,   but there wasn't enough content to justify keeping it.

\chapter{State Of The Art Review}

@@

    \item [MySQL] The schema used with the MySQL database is undocumented,
        but at least it is possible to discover the schema if one has an
        existing \acronym{SQL} database, unlike with Berkeley DB\@; all
        \acronym{SQL} databases embed the schema into the database and
        provide commands for displaying it.  Berkeley DB does not embed a
        schema in its database files, because it does not need one, and
        embedding one would not provide any benefit; it only provides
        \textbf{(key, value)} pairs, so any additional structuring of the
        data is imposed by the application, and it is the responsibility of
        the author of the application to document this structure.
        \acronym['s]{LMA} MySQL support was not tested because the schema
        is not documented, and no existing database was available to
        extract the schema from, so the required database could not be
        created.

@@

\section{Sawmill Universal Log File Analysis And Reporting}

@@

>>>>

\chapter{State of the Art Review}

@@

    \item [MySQL] MySQL is a widely used, open source, relational database.
        \acronym['s]{LMA} MySQL support was not tested because the database
        schema used by \acronym{LMA} is not documented, so the required
        database could not be created.

@@

\section{Sawmill Universal Log File Analysis and Reporting}

@@

% Added because extra spacing causes the new section to be badly
% positioned.
\newpage{}
